### 2014-12-01 paper/Content/01introduction.tex
added initial table of contents. however, with rough titles.

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....

\IEEEPARstart{D}{ieses} Template gilt f\"ur IEEE journal papers, die in \LaTeX\ mit der Klasse
IEEEtran.cls geschrieben werden.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
Vielleicht k\"onnen wir ja ein sch\"ones Paper damit erstellen und uns so schon einen Pluspunkt bei der Abgabe abholen. Ich bin mir sicher, dass der Prof. Zimmermann auf sch\"ones Aussehen steht.

	\subsection{Android}

	\subsection{MVC \& MVP}

	\subsection{Problems in Android Development}

	\subsection{Motivation: MVP for Android}

	\subsection{Research Questions}

\section{Research}

\IEEEPARstart{I}{n} this chapter, the questions are answered by research. Blablablabalabalaba.

	\subsection{Android's Building Blocks}

	\subsection{Problems in Android Development (detailed)}

	\subsection{MVP's two flavors: Passive View \& Supervising Controller}

	\subsection{Approach to solving the problem}

### 2014-12-01 paper/Content/02research.tex
added initial table of contents. however, with rough titles.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals use top floats exclusively.
% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
% floats. This can be corrected via the \fnbelowfloat command of the
% stfloats package.

### 2014-12-01 paper/Content/03conclusion.tex
added initial table of contents. however, with rough titles.

\section{Conclusion}

\IEEEPARstart{U}{sing} this approach is the future of Android and makes everything better. That is because we are such cool guys and we'll become scientists in the next two years. Here are other good reasons:

	\subsection{Outlook of our approach}

	\subsection{Other people active in this context}

### 2014-12-01 paper/Content/sources.tex
added initial table of contents. however, with rough titles.

\begin{thebibliography}{1}

\bibitem{citationID}
Citation goes here. No BibTeX because it would be overkill, only disadvantage: We need to add sources in the right citation style manually.

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

### 2014-12-02 paper/chapters/introduction.tex
Introduction to Android

\section{Introduction}

\IEEEPARstart{T}{he \emph{Android}} operating system is one of the most 
commonly used in mobile industry. According to Gartner, there will be 1.1 
billion \emph{Android}-based devices sold in 2014.
\todonote{Add citation}
But it's the installed software, the so called \quotes{Applications} or 
\quotes{Apps}, that bring the actual value to an \emph{Android} device.
Software for \emph{Android} devices can be downloaded and installed via the 
\emph{Play Store}, a software distribution solution, developed by Google and 
pre-installed on every new device, which currently holds over 1.4 million 
applications (as of November 2014).
\todonote{Add citation}

For developing such an application for the \emph{Android} mobile operating 
system, Google provides a software development kit (SDK) for the programming 
language \emph{Java}. It provides access to all functionality of the 
operating system and the underlaying phone- or tablet hardware.
However, the SDK does not define a concrete software architecture, which has to 
be used for developing the application. Instead, developers are totally free in 
designing their own architecture for fitting their needs for an application.
Having the number of 1.4 million applications in mind, this fact implies that 
there are various different software architectures currently implemented, each 
of them with their pros and cons.

### 2014-12-02 paper/Content/01introduction.tex

@@
 \section{Introduction}
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps.
-% 
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
-% 
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-% 
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
 
-\IEEEPARstart{D}{ieses} Template gilt f\"ur IEEE journal papers, die in \LaTeX\ mit der Klasse
-IEEEtran.cls geschrieben werden.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
+\IEEEPARstart{T}{he \emph{Android}} operating system is one of the most 
+commonly used in mobile industry. According to Gartner, there will be 1.1 
+billion \emph{Android}-based devices sold in 2014.
+\todonote{Add citation}
+But it's the installed software, the so called \quotes{Applications} or 
+\quotes{Apps}, that bring the actual value to an \emph{Android} device.
+Software for \emph{Android} devices can be downloaded and installed via the 
+\emph{Play Store}, a software distribution solution, developed by Google and 
+pre-installed on every new device, which currently holds over 1.4 million 
+applications (as of November 2014).
+\todonote{Add citation}
+
+For developing such an application for the \emph{Android} mobile operating 
+system, Google provides a software development kit (SDK) for the programming 
+language \emph{Java}. It provides access to all functionality of the 
+operating system and the underlaying phone- or tablet hardware.
+However, the SDK does not define a concrete software architecture, which has to 
+be used for developing the application. Instead, developers are totally free in 
+designing their own architecture for fitting their needs for an application.
+Having the number of 1.4 million applications in mind, this fact implies that 
+there are various different software architectures currently implemented, each 
+of them with their pros and cons.
+
+\todo[inline]{
 Vielleicht k\"onnen wir ja ein sch\"ones Paper damit erstellen und uns so schon einen Pluspunkt bei der Abgabe abholen. Ich bin mir sicher, dass der Prof. Zimmermann auf sch\"ones Aussehen steht.
+}
 

### 2014-12-02 paper/Content/abstract.tex

\begin{abstract}
%\boldmath
The abstract goes here.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway.

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Android, Research, SWA, MVP, MVC, Kraut, R\"uben.
\end{IEEEkeywords}

### 2014-12-02 paper/Content/01introduction.tex
References for intro

@@
 commonly used in mobile industry. According to Gartner, there will be 1.1 
-billion \emph{Android}-based devices sold in 2014.
-\todonote{Add citation}
+billion \emph{Android}-based devices sold in 2014 \cite{GartnerAndroid2014}.
 But it's the installed software, the so called \quotes{Applications} or 
@@
 pre-installed on every new device, which currently holds over 1.4 million 
-applications (as of November 2014).
-\todonote{Add citation}
+applications (as of November 2014) \cite{AppBrainStats}.
 

### 2014-12-02 paper/Content/sources.tex
References for intro

@@
 
-\bibitem{citationID}
-Citation goes here. No BibTeX because it would be overkill, only disadvantage: We need to add sources in the right citation style manually.
+\bibitem{GartnerAndroid2014}
+Gartner, \emph{Gartner Says Worldwide Traditional PC, Tablet, Ultramobile and 
+Mobile Phone Shipments Are On Pace to Grow 6.9 Percent in 2014}, March 2014, 
+[Online]. http://www.gartner.com/newsroom/id/2692318 (retrieved 02-Dec-2014)
+
+\bibitem{AppBrainStats}
+App Brain, \emph{Android Statistics -- Number of Android applications}. 
+[Online].
+http://www.appbrain.com/stats/number-of-android-apps (retrieved 02-Dec-2014)
 
@@
 \end{thebibliography}
+
+\todo[inline]{
+Citation goes here. No BibTeX because it would be overkill, only disadvantage: 
+We need to add sources in the right citation style manually.
+}

### 2015-01-02 app-weather/app/src/main/java/inf/msc/yawapp/details/WeatherDetailsActivity.java
Some MVP refactorings

@@ -23,7 +23,6 @@ import inf.msc.yawapp.common.BaseModuleActivity;
 import inf.msc.yawapp.common.Intents;
 import inf.msc.yawapp.model.Location;
 import inf.msc.yawapp.model.WeatherData;
-import inf.msc.yawapp.search.SearchActivity;
 
 public class WeatherDetailsActivity extends BaseModuleActivity implements WeatherDetailsView {
 
@@ -127,7 +126,7 @@ public class WeatherDetailsActivity extends BaseModuleActivity implements Weathe
     public boolean onOptionsItemSelected(MenuItem item) {
         switch (item.getItemId()) {
             case R.id.action_search:
-                startActivity(new Intent(this, SearchActivity.class));
+                presenter.navigateToSearch(this);
                 return true;
             case R.id.action_refresh:
                 presenter.refresh();

### 2015-01-02 app-weather/app/src/main/java/inf/msc/yawapp/details/WeatherDetailsPresenter.java

@@ -1,5 +1,6 @@
 package inf.msc.yawapp.details;
 
+import android.content.Context;
 import android.os.Bundle;
 
 import inf.msc.yawapp.model.Location;
@@ -15,6 +16,8 @@ public interface WeatherDetailsPresenter {
     public void search(final String query);
 
     public void search(final Location location);
+
+    public void navigateToSearch(final Context context);
 
     public void refresh();
 

### 2015-01-02 app-weather/app/src/main/java/inf/msc/yawapp/details/WeatherDetailsPresenterImpl.java

@@ -1,5 +1,6 @@
 package inf.msc.yawapp.details;
 
+import android.content.Context;
 import android.os.Bundle;
 
 import javax.inject.Inject;
@@ -10,6 +11,7 @@ import inf.msc.yawapp.model.Location;
 import inf.msc.yawapp.model.WeatherData;
 import inf.msc.yawapp.model.WeatherDataListener;
 import inf.msc.yawapp.model.WeatherSearchInteractor;
+import inf.msc.yawapp.navigation.NavigationPresenter;
 
 public class WeatherDetailsPresenterImpl implements WeatherDetailsPresenter, WeatherDataListener {
 
@@ -26,6 +28,9 @@ public class WeatherDetailsPresenterImpl implements WeatherDetailsPresenter, Wea
 
     @Inject
     FavouritesStore favouritesStore;
+
+    @Inject
+    NavigationPresenter navigationPresenter;
 
     private enum ViewState {
         UNINITIALIZED, LOADING, WEATHER, ERROR
@@ -100,6 +105,11 @@ public class WeatherDetailsPresenterImpl implements WeatherDetailsPresenter, Wea
         viewState = ViewState.LOADING;
         view.showLoadingAnimation();
         weatherSearchInteractor.search(location, this);
+    }
+
+    @Override
+    public void navigateToSearch(Context context) {
+        navigationPresenter.navigateSearch(context);
     }
 
     @Override

### 2015-01-02 app-weather/app/src/main/java/inf/msc/yawapp/favourites/FavouritesActivity.java

@@ -1,6 +1,5 @@
 package inf.msc.yawapp.favourites;
 
-import android.content.Intent;
 import android.os.Bundle;
 import android.os.Handler;
 import android.view.Menu;
@@ -17,7 +16,6 @@ import javax.inject.Inject;
 import inf.msc.yawapp.R;
 import inf.msc.yawapp.common.BaseModuleActivity;
 import inf.msc.yawapp.model.Location;
-import inf.msc.yawapp.search.SearchActivity;
 
 public class FavouritesActivity extends BaseModuleActivity implements FavouritesView {
 
@@ -76,7 +74,7 @@ public class FavouritesActivity extends BaseModuleActivity implements Favourites
     public boolean onOptionsItemSelected(MenuItem item) {
         switch (item.getItemId()) {
             case R.id.action_search:
-                startActivity(new Intent(this, SearchActivity.class));
+                presenter.navigateToSearch(this);
                 return true;
         }
         return super.onOptionsItemSelected(item);

### 2015-01-02 app-weather/app/src/main/java/inf/msc/yawapp/favourites/FavouritesPresenter.java

@@ -1,5 +1,7 @@
 package inf.msc.yawapp.favourites;
 
+import android.content.Context;
+
 import inf.msc.yawapp.model.Location;
 
 public interface FavouritesPresenter {
@@ -10,4 +12,6 @@ public interface FavouritesPresenter {
     public void update();
 
     public void submitSearch(final Location location);
+
+    public void navigateToSearch(final Context context);
 }

### 2015-01-02 app-weather/app/src/main/java/inf/msc/yawapp/favourites/FavouritesPresenterImpl.java

@@ -1,5 +1,7 @@
 package inf.msc.yawapp.favourites;
 
+import android.content.Context;
+
 import javax.inject.Inject;
 
 import inf.msc.yawapp.common.GenericObservable;
@@ -7,6 +9,7 @@ import inf.msc.yawapp.common.GenericObserver;
 import inf.msc.yawapp.model.FavouritesStore;
 import inf.msc.yawapp.model.FavouritesStoreOperation;
 import inf.msc.yawapp.model.Location;
+import inf.msc.yawapp.navigation.NavigationPresenter;
 import inf.msc.yawapp.navigation.SubmitSearchInteractor;
 
 public class FavouritesPresenterImpl implements FavouritesPresenter, GenericObserver<FavouritesStoreOperation> {
@@ -22,6 +25,9 @@ public class FavouritesPresenterImpl implements FavouritesPresenter, GenericObse
 
     @Inject
     SubmitSearchInteractor submitSearchInteractor;
+
+    @Inject
+    NavigationPresenter navigationPresenter;
 
     @Override
     public void init() {
@@ -42,6 +48,11 @@ public class FavouritesPresenterImpl implements FavouritesPresenter, GenericObse
     @Override
     public void submitSearch(Location location) {
         submitSearchInteractor.submitSearch(location);
+    }
+
+    @Override
+    public void navigateToSearch(Context context) {
+        navigationPresenter.navigateSearch(context);
     }
 
     @Override

### 2015-01-02 app-weather/app/src/main/java/inf/msc/yawapp/map/MapActivity.java

@@ -1,6 +1,5 @@
 package inf.msc.yawapp.map;
 
-import android.content.Intent;
 import android.os.Bundle;
 import android.view.Menu;
 import android.view.MenuItem;
@@ -18,9 +17,8 @@ import javax.inject.Inject;
 
 import inf.msc.yawapp.R;
 import inf.msc.yawapp.common.BaseModuleActivity;
-import inf.msc.yawapp.search.SearchActivity;
 
-public class MapActivity extends BaseModuleActivity implements GoogleMap.OnMapLongClickListener, GoogleMap.OnMarkerClickListener {
+public class MapActivity extends BaseModuleActivity implements MapView, GoogleMap.OnMapLongClickListener, GoogleMap.OnMarkerClickListener {
 
     @Inject
     MapPresenter presenter;
@@ -51,7 +49,7 @@ public class MapActivity extends BaseModuleActivity implements GoogleMap.OnMapLo
     public boolean onOptionsItemSelected(MenuItem item) {
         switch (item.getItemId()) {
             case R.id.action_search:
-                startActivity(new Intent(this, SearchActivity.class));
+                presenter.navigateToSearch(this);
                 return true;
         }
         return super.onOptionsItemSelected(item);
@@ -59,16 +57,12 @@ public class MapActivity extends BaseModuleActivity implements GoogleMap.OnMapLo
 
     @Override
     protected List<Object> getModules() {
-        return Arrays.<Object>asList(new MapModule());
+        return Arrays.<Object>asList(new MapModule(this));
     }
 
     @Override
     public void onMapLongClick(LatLng latLng) {
-        if (mapMarker != null) {
-            mapMarker.remove();
-        }
-        mapMarker = mapFragment.getMap().addMarker(new MarkerOptions().position(latLng));
-
+        presenter.mark((float) latLng.latitude, (float) latLng.longitude);
     }
 
     @Override
@@ -76,5 +70,18 @@ public class MapActivity extends BaseModuleActivity implements GoogleMap.OnMapLo
         LatLng latLng = marker.getPosition();
         presenter.submitSearch((float) latLng.latitude, (float) latLng.longitude);
         return true;
+    }
+
+    @Override
+    public void removeMarkers() {
+        if (mapMarker != null) {
+            mapMarker.remove();
+        }
+    }
+
+    @Override
+    public void showMarkerAt(float latitude, float longitude) {
+        LatLng position = new LatLng(latitude, longitude);
[…]

### 2015-01-02 app-weather/app/src/main/java/inf/msc/yawapp/map/MapModule.java

@@ -13,6 +13,18 @@ import dagger.Provides;
 )
 public class MapModule {
 
+    private final MapView view;
+
+    public MapModule(MapView view) {
+        this.view = view;
+    }
+
+    @Provides
+    @Singleton
+    public MapView provideMapView() {
+        return view;
+    }
+
     @Provides
     @Singleton
     public MapPresenter provideMapPresenter(MapPresenterImpl presenter) {

### 2015-01-02 app-weather/app/src/main/java/inf/msc/yawapp/map/MapPresenter.java

@@ -1,5 +1,11 @@
 package inf.msc.yawapp.map;
 
+import android.content.Context;
+
 public interface MapPresenter {
+    public void mark(float latitude, float longitude);
+
     public void submitSearch(float latitude, float longitude);
+
+    public void navigateToSearch(final Context context);
 }

### 2015-01-02 app-weather/app/src/main/java/inf/msc/yawapp/map/MapPresenterImpl.java

@@ -1,16 +1,25 @@
 package inf.msc.yawapp.map;
 
+import android.content.Context;
+
 import java.io.Serializable;
 
 import javax.inject.Inject;
 
 import inf.msc.yawapp.model.Location;
+import inf.msc.yawapp.navigation.NavigationPresenter;
 import inf.msc.yawapp.navigation.SubmitSearchInteractor;
 
 public class MapPresenterImpl implements MapPresenter {
 
     @Inject
+    MapView view;
+
+    @Inject
     SubmitSearchInteractor submitSearchInteractor;
+
+    @Inject
+    NavigationPresenter navigationPresenter;
 
     static private class LngLatLocation implements Location, Serializable {
 
@@ -49,7 +58,18 @@ public class MapPresenterImpl implements MapPresenter {
     }
 
     @Override
+    public void mark(float latitude, float longitude) {
+        view.removeMarkers();
+        view.showMarkerAt(latitude, longitude);
+    }
+
+    @Override
     public void submitSearch(final float latitude, final float longitude) {
         submitSearchInteractor.submitSearch(new LngLatLocation(latitude, longitude));
+    }
+
+    @Override
+    public void navigateToSearch(Context context) {
+        navigationPresenter.navigateSearch(context);
     }
 }

### 2015-01-02 app-weather/app/src/main/java/inf/msc/yawapp/map/MapView.java

@@ -1,0 +1,7 @@
+package inf.msc.yawapp.map;
+
+public interface MapView {
+    public void removeMarkers();
+
+    public void showMarkerAt(float latitude, float longitude);
+}

### 2015-01-02 app-weather/app/src/main/java/inf/msc/yawapp/navigation/NavigationPresenter.java

@@ -4,4 +4,6 @@ import android.content.Context;
 
 public interface NavigationPresenter {
     public boolean navigate(NavDrawerItem item, Context context);
+
+    public void navigateSearch(Context context);
 }

### 2015-01-02 app-weather/app/src/main/java/inf/msc/yawapp/navigation/NavigationPresenterImpl.java

@@ -5,6 +5,7 @@ import android.content.Intent;
 
 import inf.msc.yawapp.favourites.FavouritesActivity;
 import inf.msc.yawapp.map.MapActivity;
+import inf.msc.yawapp.search.SearchActivity;
 
 public class NavigationPresenterImpl implements NavigationPresenter {
 
@@ -24,5 +25,11 @@ public class NavigationPresenterImpl implements NavigationPresenter {
                 return false;
         }
         return true;
+    }
+
+    @Override
+    public void navigateSearch(Context context) {
+        Intent intent = new Intent(context, SearchActivity.class);
+        context.startActivity(intent);
     }
 }

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/ApplicationTest.java
First tests

@@ -1,4 +1,4 @@
-package inf.msc.yawapp;
+package inf.msc.yawapp.test;
 
 import android.app.Application;
 import android.test.ApplicationTestCase;

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/MockNavigationPresenter.java

@@ -1,0 +1,18 @@
+package inf.msc.yawapp.test;
+
+import android.content.Context;
+
+import inf.msc.yawapp.navigation.NavDrawerItem;
+import inf.msc.yawapp.navigation.NavigationPresenter;
+
+public class MockNavigationPresenter implements NavigationPresenter {
+    @Override
+    public boolean navigate(NavDrawerItem item, Context context) {
+        return false;
+    }
+
+    @Override
+    public void navigateSearch(Context context) {
+
+    }
+}

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/search/MockSearchModule.java

@@ -1,0 +1,47 @@
+package inf.msc.yawapp.test.search;
+
+import javax.inject.Singleton;
+
+import dagger.Module;
+import dagger.Provides;
+import inf.msc.yawapp.navigation.NavigationPresenter;
+import inf.msc.yawapp.search.SearchActivity;
+import inf.msc.yawapp.search.SearchPresenter;
+import inf.msc.yawapp.search.SearchView;
+import inf.msc.yawapp.test.MockNavigationPresenter;
+
+@Module(
+        injects = {
+                SearchActivity.class
+        },
+        complete = false,
+        library = true
+)
+public class MockSearchModule {
+
+    private SearchActivity searchActivity;
+    private SearchPresenter searchPresenter;
+
+    public MockSearchModule(SearchActivity searchActivity, SearchPresenter searchPresenter) {
+        this.searchActivity = searchActivity;
+        this.searchPresenter = searchPresenter;
+    }
+
+    @Provides
+    @Singleton
+    public SearchView provideSearchView() {
+        return searchActivity;
+    }
+
+    @Provides
+    @Singleton
+    public SearchPresenter provideSearchPresenter() {
+        return searchPresenter;
+    }
+
+    @Provides
+    @Singleton
+    public NavigationPresenter provideNavigationPresenter() {
+        return new MockNavigationPresenter();
+    }
+}

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/search/MockSearchPresenter.java

@@ -1,0 +1,29 @@
+package inf.msc.yawapp.test.search;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import inf.msc.yawapp.search.SearchPresenter;
+
+public class MockSearchPresenter implements SearchPresenter {
+
+    public List<String> updatedSearches = new ArrayList<>();
+    public List<String> submittedSearches = new ArrayList<>();
+    public int closeCount = 0;
+
+
+    @Override
+    public void updateSearch(String query) {
+        updatedSearches.add(query);
+    }
+
+    @Override
+    public void submitSearch(String query) {
+        submittedSearches.add(query);
+    }
+
+    @Override
+    public void close() {
+        closeCount++;
+    }
+}

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/search/SearchActivityTest.java

@@ -1,0 +1,78 @@
+package inf.msc.yawapp.test.search;
+
+import android.support.v7.widget.SearchView;
+import android.test.ActivityInstrumentationTestCase2;
+import android.view.KeyEvent;
+
+import dagger.ObjectGraph;
+import inf.msc.yawapp.R;
+import inf.msc.yawapp.search.SearchActivity;
+
+public class SearchActivityTest extends ActivityInstrumentationTestCase2<SearchActivity> {
+
+    ObjectGraph objectGraph;
+    SearchActivity searchActivity;
+    MockSearchPresenter mockSearchPresenter;
+
+    public SearchActivityTest() {
+        super(SearchActivity.class);
+    }
+
+    @Override
+    public void setUp() throws Exception {
+        super.setUp();
+        searchActivity = getActivity();
+        mockSearchPresenter = new MockSearchPresenter();
+        objectGraph = ObjectGraph.create(new MockSearchModule(searchActivity, mockSearchPresenter));
+        searchActivity.setModuleGraph(objectGraph);
+    }
+
+    /**
+     * This test fires several keystrokes in a row and checks if SearchActivity behaves correctly
+     * and is calling it's presenter object.
+     * The test expects that the SearchActivity puts focus to the search field.
+     * The presenter object should be called whenever the search string changes and on submit
+     * of the search.
+     *
+     * @throws Exception
+     */
+    public void testSubmitSearch() throws Exception {
+        getInstrumentation().sendKeyDownUpSync(KeyEvent.KEYCODE_A);
+        assertEquals(1, mockSearchPresenter.updatedSearches.size());
+        assertEquals("a", mockSearchPresenter.updatedSearches.get(0));
+
+        getInstrumentation().sendKeyDownUpSync(KeyEvent.KEYCODE_B);
+        assertEquals(2, mockSearchPresenter.updatedSearches.size());
+        assertEquals("ab", mockSearchPresenter.updatedSearches.get(1));
+
+        getInstrumentation().sendKeyDownUpSync(KeyEvent.KEYCODE_C);
+        assertEquals(3, mockSearchPresenter.updatedSearches.size());
+        assertEquals("abc", mockSearchPresenter.updatedSearches.get(2));
+
+        getInstrumentation().sendKeyDownUpSync(KeyEvent.KEYCODE_ENTER);
+        assertEquals(1, mockSearchPresenter.submittedSearches.size());
+        assertEquals("abc", mockSearchPresenter.submittedSearches.get(0));
+
[…]

### 2015-01-03 app-weather/app/src/main/java/inf/msc/yawapp/common/BaseModuleActivity.java

@@ -34,8 +34,7 @@ public abstract class BaseModuleActivity extends ActionBarActivity {
     @Override
     protected void onCreate(Bundle savedInstanceState) {
         super.onCreate(savedInstanceState);
-        moduleGraph = ((MainApplication) getApplication()).createSubGraph(getModules().toArray());
-        moduleGraph.inject(this);
+        setModuleGraph(((MainApplication) getApplication()).createSubGraph(getModules().toArray()));
     }
 
     @Override
@@ -48,6 +47,11 @@ public abstract class BaseModuleActivity extends ActionBarActivity {
     protected void onDestroy() {
         super.onDestroy();
         moduleGraph = null;
+    }
+
+    public void setModuleGraph(ObjectGraph moduleGraph) {
+        this.moduleGraph = moduleGraph;
+        this.moduleGraph.inject(this);
     }
 
     protected Toolbar getActionBarToolbar() {

### 2015-01-03 app-weather/app/src/main/java/inf/msc/yawapp/common/BaseModuleFragment.java

@@ -14,14 +14,18 @@ public abstract class BaseModuleFragment extends Fragment {
     @Override
     public void onCreate(Bundle savedInstanceState) {
         super.onCreate(savedInstanceState);
-        moduleGraph = ((MainApplication) getActivity().getApplication()).createSubGraph(getModules().toArray());
-        moduleGraph.inject(this);
+        setModuleGraph(((MainApplication) getActivity().getApplication()).createSubGraph(getModules().toArray()));
     }
 
     @Override
     public void onDestroy() {
         super.onDestroy();
         moduleGraph = null;
+    }
+
+    public void setModuleGraph(ObjectGraph moduleGraph) {
+        this.moduleGraph = moduleGraph;
+        this.moduleGraph.inject(this);
     }
 
     protected abstract List<Object> getModules();

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/search/SearchActivityTest.java
More tests

@@ -3,6 +3,10 @@ package inf.msc.yawapp.test.search;
 import android.support.v7.widget.SearchView;
 import android.test.ActivityInstrumentationTestCase2;
 import android.view.KeyEvent;
+import android.widget.ListView;
+
+import java.util.Arrays;
+import java.util.List;
 
 import dagger.ObjectGraph;
 import inf.msc.yawapp.R;
@@ -66,6 +70,7 @@ public class SearchActivityTest extends ActivityInstrumentationTestCase2<SearchA
 
         // simulate close
         final SearchView searchView = (SearchView) searchActivity.findViewById(R.id.action_search);
+        assertNotNull(searchView);
         searchActivity.runOnUiThread(new Runnable() {
             @Override
             public void run() {
@@ -74,5 +79,75 @@ public class SearchActivityTest extends ActivityInstrumentationTestCase2<SearchA
         });
         getInstrumentation().waitForIdleSync();
         assertEquals(1, mockSearchPresenter.closeCount);
+    }
+
+    /**
+     * Tests if given a suggestion list is displayed correctly in the list view of the search
+     * activity. Also tests, whether clearing of the list works as expected.
+     *
+     * @throws Exception
+     */
+    public void testShowSuggestions() throws Exception {
+        ListView listView = (ListView) searchActivity.findViewById(R.id.suggestions_container);
+        assertNotNull(listView);
+
+        // Fill
+        assertEquals(0, listView.getCount());
+        final List<String> suggestions = Arrays.asList("Foo", "Bar");
+        searchActivity.runOnUiThread(new Runnable() {
+            @Override
+            public void run() {
+                searchActivity.showSuggestions(suggestions);
+            }
+        });
+        getInstrumentation().waitForIdleSync();
+        assertEquals(2, listView.getCount());
+        assertEquals("Foo", listView.getItemAtPosition(0));
+        assertEquals("Bar", listView.getItemAtPosition(1));
+
+        // Clear
+        searchActivity.runOnUiThread(new Runnable() {
+            @Override
+            public void run() {
+                searchActivity.clearSuggestions();
+            }
+        });
+        getInstrumentation().waitForIdleSync();
+        assertEquals(0, listView.getCount());
+    }
+
+    /**
+     * This test shows some suggestions and simulates a click on one of those items.
+     * This should result in a submitted search on the presenter object.
+     *
+     * @throws Exception
+     */
+    public void testClickSuggestion() throws Exception {
[…]

### 2015-01-03 app-weather/app/src/main/java/inf/msc/yawapp/common/BaseModuleActivity.java
Graph creation strategy in base module activity

@@ -28,13 +28,28 @@ public abstract class BaseModuleActivity extends ActionBarActivity {
     @Inject
     NavigationPresenter navigationPresenter;
 
+    public interface GraphCreationStrategy {
+        public ObjectGraph getModuleGraph(BaseModuleActivity activity);
+    }
+
+    private class DefaultGraphCreationStrategy implements GraphCreationStrategy {
+
+        @Override
+        public ObjectGraph getModuleGraph(BaseModuleActivity activity) {
+            return ((MainApplication) getApplication()).createSubGraph(getModules().toArray());
+        }
+    }
+
     private ObjectGraph moduleGraph;
     private Toolbar actionBarToolbar;
+    private GraphCreationStrategy graphCreationStrategy = new DefaultGraphCreationStrategy();
 
     @Override
     protected void onCreate(Bundle savedInstanceState) {
         super.onCreate(savedInstanceState);
-        setModuleGraph(((MainApplication) getApplication()).createSubGraph(getModules().toArray()));
+        if (graphCreationStrategy != null) {
+            setModuleGraph(graphCreationStrategy.getModuleGraph(this));
+        }
     }
 
     @Override
@@ -52,6 +67,10 @@ public abstract class BaseModuleActivity extends ActionBarActivity {
     public void setModuleGraph(ObjectGraph moduleGraph) {
         this.moduleGraph = moduleGraph;
         this.moduleGraph.inject(this);
+    }
+
+    public void setGraphCreationStrategy(GraphCreationStrategy graphCreationStrategy) {
+        this.graphCreationStrategy = graphCreationStrategy;
     }
 
     protected Toolbar getActionBarToolbar() {

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/ApplicationTest.java
own unit test class

@@ -1,13 +1,0 @@
-package inf.msc.yawapp.test;
-
-import android.app.Application;
-import android.test.ApplicationTestCase;
-
-/**
- * <a href="http://d.android.com/tools/testing/testing_android.html">Testing Fundamentals</a>
- */
-public class ApplicationTest extends ApplicationTestCase<Application> {
-    public ApplicationTest() {
-        super(Application.class);
-    }
-}

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/MockMainApplication.java

@@ -1,0 +1,17 @@
+package inf.msc.yawapp.test;
+
+import dagger.ObjectGraph;
+import inf.msc.yawapp.MainApplication;
+import inf.msc.yawapp.R;
+
+public class MockMainApplication extends MainApplication {
+    @Override
+    public void onCreate() {
+        setTheme(R.style.AppTheme);
+    }
+
+    @Override
+    public ObjectGraph createSubGraph(Object... modules) {
+        return ObjectGraph.create(modules);
+    }
+}

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/ModuleActivityUnitTestCase.java

@@ -1,0 +1,139 @@
+package inf.msc.yawapp.test;
+
+import android.app.Activity;
+import android.app.Application;
+import android.content.ComponentName;
+import android.content.Context;
+import android.content.Intent;
+import android.content.pm.ActivityInfo;
+import android.os.Bundle;
+import android.os.IBinder;
+import android.test.ActivityTestCase;
+import android.view.ContextThemeWrapper;
+import android.view.Window;
+
+import inf.msc.yawapp.R;
+import inf.msc.yawapp.common.BaseModuleActivity;
+
+public class ModuleActivityUnitTestCase<T extends BaseModuleActivity> extends ActivityTestCase {
+
+    private Class<T> activityClass;
+    private boolean isAttached = false;
+    private boolean isCreated = false;
+    private Application mockApplication;
+    private Context activityContext;
+    private BaseModuleActivity.GraphCreationStrategy graphCreationStrategy;
+
+    public ModuleActivityUnitTestCase(Class<T> activityClass) {
+        this.activityClass = activityClass;
+    }
+
+    protected T startActivity(Bundle savedInstanceState) {
+        if (!isAttached) {
+            assertNotNull(activityClass);
+            setActivity(null);
+            T newActivity = null;
+            try {
+                IBinder token = null;
+                if (mockApplication == null) {
+                    mockApplication = new MockMainApplication();
+                }
+                ComponentName componentName = new ComponentName(getInstrumentation().getTargetContext(), activityClass);
+                Intent startIntent = new Intent(getInstrumentation().getContext(), activityClass);
+                startIntent.setComponent(componentName);
+                ActivityInfo info = new ActivityInfo();
+                CharSequence title = activityClass.getName();
+                MockParent parent = new MockParent();
+                newActivity = (T) getInstrumentation().newActivity(
+                        activityClass, activityContext, token, mockApplication, startIntent, info,
+                        title, parent, null, null);
+            } catch (Exception e) {
+                assertNotNull(newActivity);
+            }
+            assertNotNull(newActivity);
+            setActivity(newActivity);
+            if (graphCreationStrategy != null) {
+                newActivity.setGraphCreationStrategy(graphCreationStrategy);
+            }
+            isAttached = true;
+        }
+
+        T result = getActivity();
+        if (result != null) {
+            getInstrumentation().callActivityOnCreate(getActivity(), savedInstanceState);
+            isCreated = true;
+        }
+        return result;
+    }
+
+    @Override
[…]

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/favourites/FavouritesActivityTest.java
FavouritesActivity tests

@@ -1,0 +1,118 @@
+package inf.msc.yawapp.test.favourites;
+
+import android.widget.ListView;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import dagger.ObjectGraph;
+import inf.msc.yawapp.R;
+import inf.msc.yawapp.common.BaseModuleActivity;
+import inf.msc.yawapp.favourites.FavouritesActivity;
+import inf.msc.yawapp.model.Location;
+import inf.msc.yawapp.test.ModuleActivityUnitTestCase;
+import inf.msc.yawapp.test.model.MockLocation;
+
+public class FavouritesActivityTest extends ModuleActivityUnitTestCase<FavouritesActivity> {
+
+    FavouritesActivity activity;
+    MockFavouritesPresenter presenter;
+
+    public FavouritesActivityTest() {
+        super(FavouritesActivity.class);
+    }
+
+    @Override
+    protected void setUp() throws Exception {
+        super.setUp();
+        presenter = new MockFavouritesPresenter();
+        setGraphCreationStrategy(new BaseModuleActivity.GraphCreationStrategy() {
+            @Override
+            public ObjectGraph getModuleGraph(BaseModuleActivity activity) {
+                return ObjectGraph.create(new MockFavouritesModule((FavouritesActivity) activity, presenter));
+            }
+        });
+        activity = startActivity(null);
+
+        // init & update should be called during onCreate of the activity
+        assertEquals(1, presenter.initCount);
+        assertEquals(1, presenter.updateCount);
+    }
+
+    public void testFavouritesList() throws Exception {
+        ListView list = (ListView) activity.findViewById(R.id.favourites_container);
+        assertNotNull(list);
+        assertEquals(0, list.getCount());
+
+        // Prepare some "favourite" locations
+        final List<Location> testLocations = new ArrayList<>();
+        MockLocation testLocation;
+        testLocation = new MockLocation();
+        testLocation.id = 1;
+        testLocation.city = "Paradise City";
+        testLocation.country = "Heaven";
+        testLocation.latitude = .1f;
+        testLocation.longitude = .2f;
+        testLocations.add(testLocation);
+        testLocation = new MockLocation();
+        testLocation.id = 2;
+        testLocation.city = "Somewhere";
+        testLocation.country = "Over the rainbow";
+        testLocation.latitude = 3.f;
+        testLocation.longitude = 4.f;
+        testLocations.add(testLocation);
+
+        activity.runOnUiThread(new Runnable() {
+            @Override
+            public void run() {
[…]

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/favourites/MockFavouritesModule.java

@@ -1,0 +1,47 @@
+package inf.msc.yawapp.test.favourites;
+
+import javax.inject.Singleton;
+
+import dagger.Module;
+import dagger.Provides;
+import inf.msc.yawapp.favourites.FavouritesActivity;
+import inf.msc.yawapp.favourites.FavouritesPresenter;
+import inf.msc.yawapp.favourites.FavouritesView;
+import inf.msc.yawapp.navigation.NavigationPresenter;
+import inf.msc.yawapp.test.MockNavigationPresenter;
+
+@Module(
+        injects = {
+                FavouritesActivity.class
+        },
+        complete = false,
+        library = true
+)
+public class MockFavouritesModule {
+
+    private FavouritesActivity favouritesActivity;
+    private FavouritesPresenter favouritesPresenter;
+
+    public MockFavouritesModule(FavouritesActivity favouritesActivity, FavouritesPresenter favouritesPresenter) {
+        this.favouritesActivity = favouritesActivity;
+        this.favouritesPresenter = favouritesPresenter;
+    }
+
+    @Provides
+    @Singleton
+    public FavouritesView provideFavouritesView() {
+        return favouritesActivity;
+    }
+
+    @Provides
+    @Singleton
+    public FavouritesPresenter provideFavouritesPresenter() {
+        return favouritesPresenter;
+    }
+
+    @Provides
+    @Singleton
+    public NavigationPresenter provideNavigationPresenter() {
+        return new MockNavigationPresenter();
+    }
+}

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/favourites/MockFavouritesPresenter.java

@@ -1,0 +1,43 @@
+package inf.msc.yawapp.test.favourites;
+
+import android.content.Context;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import inf.msc.yawapp.favourites.FavouritesPresenter;
+import inf.msc.yawapp.model.Location;
+
+public class MockFavouritesPresenter implements FavouritesPresenter {
+
+    public int initCount = 0;
+    public int deinitCount = 0;
+    public int updateCount = 0;
+    public List<Location> submitSearchList = new ArrayList<>();
+    public List<Context> navigateToSearchList = new ArrayList<>();
+
+    @Override
+    public void init() {
+        initCount++;
+    }
+
+    @Override
+    public void deinit() {
+        deinitCount++;
+    }
+
+    @Override
+    public void update() {
+        updateCount++;
+    }
+
+    @Override
+    public void submitSearch(Location location) {
+        submitSearchList.add(location);
+    }
+
+    @Override
+    public void navigateToSearch(Context context) {
+        navigateToSearchList.add(context);
+    }
+}

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/model/MockLocation.java

@@ -1,0 +1,37 @@
+package inf.msc.yawapp.test.model;
+
+import inf.msc.yawapp.model.Location;
+
+public class MockLocation implements Location {
+
+    public long id;
+    public String city;
+    public String country;
+    public float latitude;
+    public float longitude;
+
+    @Override
+    public long getId() {
+        return id;
+    }
+
+    @Override
+    public String getCity() {
+        return city;
+    }
+
+    @Override
+    public String getCountry() {
+        return country;
+    }
+
+    @Override
+    public float getLatitude() {
+        return latitude;
+    }
+
+    @Override
+    public float getLongitude() {
+        return longitude;
+    }
+}

### 2015-01-03 app-weather/app/src/main/java/inf/msc/yawapp/favourites/FavouritesActivity.java
Fixed FavouritesActivity: removed useless handler on item click

@@ -44,12 +44,7 @@ public class FavouritesActivity extends BaseModuleActivity implements Favourites
             @Override
             public void onItemClick(AdapterView<?> parent, View view, int position, long id) {
                 final Location item = (Location) parent.getItemAtPosition(position);
-                new Handler().post(new Runnable() {
-                    @Override
-                    public void run() {
-                        presenter.submitSearch(item);
-                    }
-                });
+                presenter.submitSearch(item);
             }
         });
 

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/ModuleActivityUnitTestCase.java
comments

@@ -15,6 +15,16 @@ import android.view.Window;
 import inf.msc.yawapp.R;
 import inf.msc.yawapp.common.BaseModuleActivity;
 
+/**
+ * Unit test case class for BaseModuleActivities
+ * <p/>
+ * This class was created due to a bug in the ActivityUnitTestCase class of the android test
+ * framework (Issue no. 22737: https://code.google.com/p/android/issues/detail?id=22737).
+ * The ActivityUnitTestCase class does not work with activities in sub-packages.
+ *
+ * @param <T>
+ */
+@SuppressWarnings("unchecked")
 public class ModuleActivityUnitTestCase<T extends BaseModuleActivity> extends ActivityTestCase {
 
     private Class<T> activityClass;
@@ -29,6 +39,8 @@ public class ModuleActivityUnitTestCase<T extends BaseModuleActivity> extends Ac
     }
 
     protected T startActivity(Bundle savedInstanceState) {
+        assertFalse("Activity already created", isCreated);
+
         if (!isAttached) {
             assertNotNull(activityClass);
             setActivity(null);
@@ -96,6 +108,9 @@ public class ModuleActivityUnitTestCase<T extends BaseModuleActivity> extends Ac
         this.activityContext = activityContext;
     }
 
+    /**
+     * Copied from ActivityUnitTestCase
+     */
     private static class MockParent extends Activity {
 
         public int requestedOrientation = 0;

### 2015-01-03 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/favourites/FavouritesActivityTest.java

@@ -39,6 +39,13 @@ public class FavouritesActivityTest extends ModuleActivityUnitTestCase<Favourite
         assertEquals(1, presenter.updateCount);
     }
 
+    /**
+     * This test fills the favourites list view with two test location objects and expects those
+     * entries to be visible in the list.
+     * Afterwards the test attempts to clear the list through the FavouritesView interface.
+     *
+     * @throws Exception
+     */
     public void testFavouritesList() throws Exception {
         ListView list = (ListView) activity.findViewById(R.id.favourites_container);
         assertNotNull(list);
@@ -62,27 +69,22 @@ public class FavouritesActivityTest extends ModuleActivityUnitTestCase<Favourite
         testLocation.longitude = 4.f;
         testLocations.add(testLocation);
 
-        activity.runOnUiThread(new Runnable() {
-            @Override
-            public void run() {
-                activity.addFavourites(testLocations);
-            }
-        });
-        getInstrumentation().waitForIdleSync();
+        activity.addFavourites(testLocations);
         assertEquals(2, list.getCount());
         assertEquals("Paradise City", ((Location) list.getItemAtPosition(0)).getCity());
 
         // Clear list
-        activity.runOnUiThread(new Runnable() {
-            @Override
-            public void run() {
-                activity.clearView();
-            }
-        });
-        getInstrumentation().waitForIdleSync();
+        activity.clearView();
         assertEquals(0, list.getCount());
     }
 
+    /**
+     * Gives a test location object to the activity and simulates a click on that item in the
+     * favourites list. The test expects the presenter to be called once with exactly the same
+     * location object given to the view.
+     *
+     * @throws Exception
+     */
     public void testFavouritesListClick() throws Exception {
         final ListView list = (ListView) activity.findViewById(R.id.favourites_container);
         assertNotNull(list);
@@ -96,23 +98,24 @@ public class FavouritesActivityTest extends ModuleActivityUnitTestCase<Favourite
         testLocation.city = "Paradise City";
         testLocations.add(testLocation);
 
-        activity.runOnUiThread(new Runnable() {
-            @Override
-            public void run() {
-                activity.addFavourites(testLocations);
-            }
-        });
-        getInstrumentation().waitForIdleSync();
+        // Give the location to the activity through the FavouritesView interface
+        activity.addFavourites(testLocations);
         assertEquals(1, list.getCount());
 
[…]

### 2015-01-05 paper/Content/02research.tex
Android building blocks / components

@@
 % stfloats package.
+
+\section{Research}
+
+\IEEEPARstart{I}{n} this chapter, the questions are answered by research. Blablablabalabalaba.
+
+\subsection{Components of an \emph{Android} Application}
+
+Building an \emph{Android} application requires several core components of the \emph{Android} SDK to be used.
+This section gives a short overview and short explanation of the components, used for the prototype, created for this paper.
+
+\textbf{Activity}: An application typically consists of one or more activities.
+An activity fills the whole screen of the device and can be compared to a \emph{window} in a classic desktop application.
+The official \emph{Android} SDK documentation \cite{SDKActivities} defines an activity as \enquote{an application component that provides a screen with which users can interact in order to do something}.
+There is a defined lifcycle, which all activity objects go through -- the creation, start, stop and the destruction of an activity object.
+This lifecycle is managed by \emph{Android} itself, meaning an application developer must not manually create or destroy activity objects.
+
+\textbf{Fragment}: Fragment split more complex parts of an activity's user interface into several smaller sub-components.
+Fragments are also used to encapsulate reusable parts of the user interface, which for example need to appear in mulitple activities.
+The official documentation of the \emph{Android} SDK defines a fragment as follows \cite{SDKFragments}:
+
+\begin{quote}
+A Fragment represents a behavior or a portion of user interface in an Activity.
+You can combine multiple fragments in a single activity to build a multi-pane UI and reuse a fragment in multiple activities.
+\end{quote}
+
+\subsection{Problems in Android Development (detailed)}
+
+\subsection{MVP's two flavors: Passive View \& Supervising Controller}
+
+\subsection{Approach to solving the problem}

### 2015-01-08 paper/Content/01introduction.tex
Android building blocks / components
paper introduction drafted. resources added, title changed.

@@
 \IEEEPARstart{T}{he \emph{Android}} operating system is one of the most 
-commonly used in mobile industry. According to Gartner, there will be 1.1 
-billion \emph{Android}-based devices sold in 2014 \cite{GartnerAndroid2014}.
-But it's the installed software, the so called \quotes{Applications} or 
-\quotes{Apps}, that bring the actual value to an \emph{Android} device.
+commonly used in mobile industry.
+After its first presentation in 2007, the open source system started its successful journey and became the leading mobile operating system in 2010 \cite{PassiveMVC}.
+According to Gartner \cite{GartnerAndroid2014}, there will be 1.1 billion \emph{Android}-based devices sold in 2014.
+
+What brings the actual value to an \emph{Android} device is the installed software, the so called \quotes{Applications} or 
+\quotes{Apps}.
 Software for \emph{Android} devices can be downloaded and installed via the 
@@
 pre-installed on every new device, which currently holds over 1.4 million 
-applications (as of November 2014) \cite{AppBrainStats}.
+applications (as of November 2014) \cite{AppBrainStats}.\\
+
+%\subsection{Application Development}
 
@@
 language \emph{Java}. It provides access to all functionality of the 
-operating system and the underlaying phone- or tablet hardware.
-However, the SDK does not define a concrete software architecture, which has to 
-be used for developing the application. Instead, developers are totally free in 
+operating system and the underlaying phone- or tablet hardware. The principle components of the \emph{Android} SDK are explained later in this document.\\
+
+%\subsection{Challenges in Android Development}
+
+The SDK does not define a specific software architecture which has to 
+be used for developing the application \cite{AndroidDeveloperCollection}. Instead, developers are totally free in 
 designing their own architecture for fitting their needs for an application.
@@
 
-\todo[inline]{
-Vielleicht k\"onnen wir ja ein sch\"ones Paper damit erstellen und uns so schon einen Pluspunkt bei der Abgabe abholen. Ich bin mir sicher, dass der Prof. Zimmermann auf sch\"ones Aussehen steht.
-}
+However, not having clear rules regarding the application's architecture entails risks, especially for people that are not expert-level developers.
+Applications become larger from time to time, and without a reasonable architecture this leads to complex code which is hard to understand and maintain \cite{PassiveMVC, BallOfMud}.
+Additionally, complex dependencies in the SDK cause messy code and make it hard to exchange specific elements without affecting other elements \cite{PassiveMVC}.\\ \todo[inline]{Testability einfügen -- Wie lässt sich das Problem zusammenfassen?}
 
-	\subsection{Android}
+%\subsection{Model-View-Presenter Architecture}
 
-	\subsection{MVC \& MVP}
+A modern architecture approach is Model-View-Presenter (MVP), a model introduced in 1996 to support event-driven systems \cite{TaligentMVP}.
+Its main goal is to separate the data logic from the presentation logic, thus creating software which is more flexible in terms of replacing the data model without changing the presentation part or vice versa \cite{PassiveMVC}.
+Therefor, the software is split into three parts: The \emph{Model} provides the data and means to manipulate it, the \emph{View} part is responsible to display the data, and the \emph{Presenter} contains the business logic that handles user-initiated events and issues the appropriate manipulation of the data \cite{TaligentMVP}.\\
 
-	\subsection{Problems in Android Development}
+%\subsection{Applying MVP in Android}
 
-	\subsection{Motivation: MVP for Android}
+Applying MVP to \emph{Android} applications seems promising to build less complex applications with clear code and improved extensibility.
+However, as the considerations in this paper show, an \emph{Android} implementation of MVP is tricky.
+Some components of the SDK have several responsibilities and make it hard to define whether they are a \emph{Model}, a \emph{View} or a \emph{Presenter} \cite{PassiveMVC}.
 
-	\subsection{Research Questions}
+The approach developed in this paper aims to clarify the distinction of these architectural parts.
+The findings of our research may serve as a guideline on how to apply MVP in \emph{Android} application development.\\
 
-\section{Research}
+%\subsection{Research Questions}
+In the following sections, these questions concerning the application of MVP to \emph{Android} application development are evaluated and answered:
 
-\IEEEPARstart{I}{n} this chapter, the questions are answered by research. Blablablabalabalaba.
+\begin{enumerate}[label={RQ\arabic*:}, leftmargin=0.95cm]
+\item What are the inherent characteristics given / recommended by the Android Framework? What is the current state in Android Development in accordance to the inherent framework characteristics?
+\item What are the key benefits of the Model-View-Presenter approach?
+\item How can the MVP model be applied to the Android App architecture considering framework building blocks?
+\end{enumerate}
 
-	\subsection{Android's Building Blocks}
-
-	\subsection{Problems in Android Development (detailed)}
-
-	\subsection{MVP's two flavors: Passive View \& Supervising Controller}
-
-	\subsection{Approach to solving the problem}
+To answer these questions, a prototypical App is built using the MVP approach.
+\todo[inline]{Outlook for each chapter?}

### 2015-01-08 paper/Content/abstract.tex
paper introduction drafted. resources added, title changed.

@@
 %\boldmath
-The abstract goes here.
+Minions ipsum me want bananaaa!
+Hahaha chasy hana dul sae belloo!
+Aaaaaah daa ti aamoo!
+La bodaaa pepete.
+La bodaaa para tú gelatooo underweaaar po kass tank yuuu!
+Underweaaar.
+Wiiiii bappleees jiji chasy underweaaar.
+Tank yuuu!
+jeje me want bananaaa!
+Me want bananaaa!
+Hahaha aaaaaah chasy hana dul sae gelatooo jeje tulaliloo.
+Baboiii bappleees wiiiii daa underweaaar tank yuuu!
+Underweaaar.
+Jiji potatoooo butt la bodaaa ti aamoo!
+Para tú tatata bala tu.
+Jiji underweaaar bappleees belloo!
+La bodaaa.
+Bee do bee do bee do jiji tatata bala tu belloo!
+Gelatooo bappleees hana dul sae ti aamoo!
+
+Poopayee bappleees underweaaar bee do bee do bee do.
+Hana dul sae potatoooo bappleees la bodaaa baboiii.
+Pepete para tú hana dul sae tank yuuu!
+Jiji poulet tikka masala tatata bala tu ti aamoo!
+Po kass belloo!
+Wiiiii daa me want bananaaa!
+Chasy poopayee jeje po kass.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Android, Research, SWA, MVP, MVC, Kraut, R\"uben.
+Android,  Application Architecture, Model-View-Presenter (MVP), App Prototype.
 \end{IEEEkeywords}

### 2015-01-08 paper/Content/sources.tex
paper introduction drafted. resources added, title changed.

--- 2014-12-01 paper/Content/sources.tex
@@
 
-\bibitem{citationID}
-Citation goes here. No BibTeX because it would be overkill, only disadvantage: We need to add sources in the right citation style manually.
+\bibitem{PassiveMVC}
+K.
+Sokolova, M.
+Lemercier, and L.
+Garcia: \emph{Android Passive MVC: a Novel Architecture Model for Android Application Development.} In: PATTERNS 2013, The Fifth International Conferences on Pervasive Patterns and Applications, p.
+7-12, 2013.
 
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+\bibitem{GartnerAndroid2014}
+Gartner: \emph{Gartner Says Worldwide Traditional PC, Tablet, Ultramobile and 
+Mobile Phone Shipments Are On Pace to Grow 6.9 Percent in 2014}, March 2014, 
+[Online]. http://www.gartner.com/newsroom/id/2692318 (retrieved 02-Dec-2014)
+
+\bibitem{AppBrainStats}
+App Brain: \emph{Android Statistics -- Number of Android applications}. 
+[Online].
+http://www.appbrain.com/stats/number-of-android-apps (retrieved 02-Dec-2014)
+
+\bibitem{AndroidDeveloperCollection}
+J. Steele, N. To, S. Conder, and L. Darcey: \emph{The Android Developer's Collection.} Addison-Wesley Professional, December 2011.
+
+\bibitem{BallOfMud}
+B. Foote and J. Yoder: \emph{Big Ball of Mud.} Addison-Wesley, 1997.
+
+\bibitem{TaligentMVP}
+M. Potel: \emph{MVP: Model-View-Presenter the taligent programming model for C++ and Java}, Taligent Inc., 1996.
+
+\bibitem{GangOfFour}
+E. Gamma, R. Helm, R. Johnson, and J. Vlissides: \emph{Design Patterns: Elements of Reusable Object-Oriented Software,} 1\textsuperscript{st} ed. Addison-Wesley Professional, November 1994.
+
+%\bibitem{}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
 

### 2015-01-09 paper/Content/01introduction.tex
updated introduction.

@@
 Applications become larger from time to time, and without a reasonable architecture this leads to complex code which is hard to understand and maintain \cite{PassiveMVC, BallOfMud}.
-Additionally, complex dependencies in the SDK cause messy code and make it hard to exchange specific elements without affecting other elements \cite{PassiveMVC}.\\ \todo[inline]{Testability einfügen -- Wie lässt sich das Problem zusammenfassen?}
+Additionally, complex dependencies in the SDK cause messy code and make it hard to exchange specific elements without affecting other elements \cite{PassiveMVC}.
+That is especially because \emph{Android} tends to lead to classes containing a lot of functionality, which often requires more effort concerning testability and extendability \cite{GangOfFour}.
+\\
 

### 2015-01-09 paper/Content/03conclusion.tex
Conclusion

@@
 
-\IEEEPARstart{U}{sing} this approach is the future of Android and makes everything better.
-That is because we are such cool guys and we'll become scientists in the next two years.
-Here are other good reasons:
+\IEEEPARstart{I}{n} course of this research paper we have analyzed the characteristics given by the \emph{Android} Framework and have identified 
+principle components which are generally used for developing an \emph{Android} applications. Those components have been examined regarding their composition and characteristics. 
+Applying MVP offers various benefits like a better testability [……], but the paper has shown that it is often hard to define the roles 
+of the \emph{Android} components considering MVP and to embed those components into the whole MVP model. But finally we can offer an MVP approach 
+for \emph{Android} and a corresponding prototype app demonstrating how principle \emph{Android} components can be structured for applying MVP.
 
-	\subsection{Outlook of our approach}
+However, just the essential framework components have been examined regarding their MVP compatibility and used in the prototype. 
+The MVP pattern for \emph{Android} would only succeed in practice if a wide bandwidth of framework components was adaptable. 
+In course of additional research studies addressing this topic we recommend to examine further frameworks components and 
+evaluate them regarding their MVP compatibility by implementing prototypes.
 
-	\subsection{Other people active in this context}
+There are further and particularly similar MVP approaches developed and provided by the \emph{Android} developer community. 
+\emph{Google} developer \emph{Chris Banes} has developed the \emph{Android} app \emph{philm} basing on MVP. 
+The very demonstrative source code is offered on \emph{github} [https://github.com/chrisbanes/philm] and worth seeing. 
+Moreover there is a huge developer community on \emph{Google+} [https://plus.google.com/communities/114285790907815804707] dealing with different MVP approaches. 
+Finally, we want to draw your attention to the paper \emph{Android Passive MVC: a Novel Architecture Model for Android Application Development} 
+[Quelle] which is worth reading and has been an inspiration for our approach. Although the paper proposes an architecture which is rather MVC than MVP-based, 
+it offers an interesting approach how the components of an \emph{Android} app can be organized for building an MV-x structure.

### 2015-01-09 paper/Content/sources.tex
Added missing sources for 'building blocks'

@@
 
+\bibitem{SDKActivities}
+Google Inc., \emph{Android Developers -- Activities},
+[Online]. http://developer.android.com/guide/components/activities.html (retrieved 05-Jan-2015)
+
+\bibitem{SDKFragments}
+Google Inc., \emph{Android Developers -- Fragments},
+[Online]. http://developer.android.com/guide/components/fragments.html(retrieved 05-Jan-2015)
+
 \bibitem{BallOfMud}

### 2015-01-10 paper/Content/sources.tex
Added Fowler; added MVP UML-like graphic

@@
 
+\bibitem{FowlerMvpRetirementNote}
+Fowler, Martin: \emph{Retirement note for Model View Presenter Pattern},
+[Online]. http://martinfowler.com/eaaDev/ModelViewPresenter.html (retrieved 10-Jan-2015)
+
+\bibitem{FowlerSupervisingController}
+Fowler, Martin: \emph{Supervising Controller},
+[Online]. http://martinfowler.com/eaaDev/SupervisingPresenter.html (retrieved 10-Jan-2015)
+
+\bibitem{FowlerPassiveView}
+Fowler, Martin: \emph{Passive View},
+[Online]. http://martinfowler.com/eaaDev/PassiveScreen.html (retrieved 10-Jan-2015)
+
 %\bibitem{}

### 2015-01-10 paper/Content/02research.tex
Added missing sources for 'building blocks'
Added Fowler; added MVP UML-like graphic
MVP explained in general

@@
 
-\textbf{Fragment}: Fragment split more complex parts of an activity's user interface into several smaller sub-components.
+\textbf{Fragment}: Fragments split more complex parts of an activity's user interface into several smaller sub-components.
 Fragments are also used to encapsulate reusable parts of the user interface, which for example need to appear in mulitple activities.
@@
 
+The \emph{Model-View-Presenter} (MVP) pattern was introduced in 1996 by Potel \cite{TaligentMVP} while developing a programming model for multi-tier client/server applications.
+Potel explains in his paper how to generalize the classical \emph{Model-View-Controller} (MVC) approach in order to build more complex applications.
+His idea was to decompose the MVC approach into two fundamental concepts: Data Management (Model) and User Interface (View-Controller).
+
+Like in MVC, Potel's \emph{Model-View-Presenter} pattern consists of three components: \emph{Model}, \emph{View} and \emph{Presenter}.
+The \emph{Model} represents the domain model including the business logic.
+The \emph{View} represents the user interface and interacts with the user and shows the data from the model in a certain way.
+The \emph{Presenter} is the mediator between the business logic (Model) and the user interface (View).
+Its responsibility is to prepare the data (presentation logic) in order to show it in the user interface and vice versa, to determine how user interactions are going to change the model.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=0.5\textwidth]{Images/mvp}
+\caption{Supervising Controller and Passive View}
+\label{fig:mvp}
+\end{figure}
+
+Today, when we talk about MVP, we are talking about two different types: \emph{Supervising Controller} \cite{FowlerSupervisingController} and \emph{Passive View} \cite{FowlerPassiveView}.
+Fowler retired the classic MVP approach in 2006 \cite{FowlerMvpRetirementNote} and introduced those two implementations -- see Figure \ref{fig:mvp}.
+
+The \textbf{Supervising Controller} approach splits the User Interface in two components: a \emph{Presenter} and \emph{View} – like the classical MVP approach.
+The \emph{Model} can communicate changes to the \emph{View} using an Observer pattern (indirectly shown as dotted lines in Figure \ref{fig:mvp}).
+The \emph{View} can make direct changes to the model.
+In most cases this is done by simple mappings and \emph{Data Binding} capabilities provided by UI frameworks.
+Any user input is handled by the \emph{Presenter}.
+It determines how those interactions affect the underlying \emph{Model}.
+In addition, it handles complex view logic operations i.e.
+to prepare the model data for the view layer or vice versa, to transform the user input to fit the model requirements.
+
+In contrast to the Supervising Controller, the \textbf{Passive View} totally separates the \emph{View} from the \emph{Model}.
+There is no direct or indirect interaction between them -- see Figure \ref{fig:mvp}.
+Interactions between \emph{View} and \emph{Model} is done exclusively via the \emph{Presenter}.
+This approach reduces the \emph{View} to an absolute minimum by using the \emph{Presenter} to handle all user input events, to update the \emph{Model} based on user interactions as well as to channel \emph{Model} changes back to the \emph{View}.
+As a result, the \emph{View} is made completely passive and is no longer responsible for updating itself from the \emph{Model}.\\
+The primary driver for \emph{Passive View} is testing. This concept allows testing to be focused on the \emph{Presenter} without needing any interaction with the chosen UI framework.
+
 \subsection{Approach to solving the problem}

### 2015-01-10 paper/Content/solution.tex
Solution chapter

\section{Android App Prototype}

The prototype Android app, developed for this paper, is a simple weather app. It is able to show the current weather data for a location including temperature, humidity and wind. For retrieving this data, the app connects to the remote \emph{application programming interface} (API) of \emph{openweathermap.org}, a free-to-use service for retrieving weather data. The app also manages a list of favourite locations. Locations can either be specified using a free-text search field or by pointing locations on a map, for which the \emph{Google Maps} API was used.

As mentioned above, the basic building blocks of an Android application are \emph{Activities} and \emph{Fragments}. Applying MVP to an Android application therefore means to put attention on those components.

The implementation of MVP in the app prototype, follows the approach of Leiva \cite{AntLeiv14}, in which \emph{Activities} implement the view part. This means that in addition to extending the base Android \texttt{Activity} class, an activity class must also implement a \texttt{View} interface. The class structure around such an activity is illustrated in Fig. \ref{fig:androidmvp}.

\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{diag1.pdf}
\caption{Class structure of an activity (highlighted with yellow background) in the context of an MVP architecture}
\label{fig:androidmvp}
\end{figure}

Each activity object has an presenter object associated, implementing the \texttt{Presenter} interface. On the other hand, the presenter object has a reference to the activity object. View related actions, like a click on a button, cause handler functions inside the \texttt{Activity} class being called. Those handler functions do nothing more than executing corresponding actions on the presenter object.

The interaction with the model is done only by the presenter. This makes the app prototype an implementation of the \emph{Passive View} kind of MVP (see \cite[p. 8]{PassiveMVC}).
An example of an interaction sequence between objects of \texttt{Activity}, \texttt{Presenter} and \texttt{Model} classes is shown in Fig. \ref{fig:androidmvpseq}. Clicking on a button -- let's assume it's labeled \emph{Refresh} -- causes the handler function in the \texttt{Activity} being called. An action is executed on the presenter object by the activity. The presenter retrieves new data from the model and afterwards calls the activity (the \texttt{View}) for showing that data.

\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{diag2.pdf}
\caption{Interaction sequence involving objects of \texttt{Activity}, \texttt{Presenter} and \texttt{Model} classes}
\label{fig:androidmvpseq}
\end{figure}

For model operations that take a while to execute -- like retrieving weather data from \emph{openweathermap.org}, which can take a few seconds -- the interaction between presenter and model was implemented in an asynchronous way. Model objects, used by multiple presenters, additionally implement the \emph{Observer} design pattern (see \cite[p. 287]{GangOfFour}) to notify all registered presenters on model changes.

The MVP pattern can be applied to \emph{Fragments} the same way as it is described above for \emph{Activities}. Presenters of \emph{Fragment} objects most likely share their model with either other \emph{Fragments} and other \emph{Activities}. An example of this was implemented in the \texttt{WeatherDetailsActivity} of the app prototype, which shows the weather data for a selected location. The part of the view showing temperature and wind information was extracted into a separate \emph{Fragment} with its own presenter implementation. Clicking on the \emph{Refresh} button causes the presenter of the activity to instruct the model to fetch updated weather data from \emph{openweathermap.org}. When this data is available, the model notifies all registered observers -- in this case the presenter of the activity and the presenter of the fragment. Both presenters go back to the corresponding view objects and cause the updated data to be displayed.

\todo[inline]{Maybe add something about Intents here}

This answers RQ3, showing that MVP can be applied to an Android application considering the \emph{Activity} and \emph{Fragment} building blocks.

As an additional remark, the usage of the \emph{Dependency Injection} (see \cite{Fowler04}) library \emph{Dagger} should be mentioned. The library was used to resolve object dependencies, like the one which exists between an \texttt{Activity} and an \texttt{Presenter} object (and vice versa). It automatically injects references of both objects into each other.

### 2015-01-10 paper/Content/sources.tex
Solution chapter

--- 2015-01-09 paper/Content/sources.tex
@@
 
+\bibitem{AntLeiv14}
+A. Leiva: \emph{MVP for Android: how to organize the presentation layer}, 2014,
+[Online]. http://antonioleiva.com/mvp-android/ (retrieved 10-Jan-2015)
+
+\bibitem{Fowler04}
+M. Fowler: \emph{Inversion of Control Containers and the Dependency Injection pattern}, 2004,
+[Online]. http://martinfowler.com/articles/injection.html (retrieved 10-Jan-2015)
+
 %\bibitem{}

### 2015-01-10 paper/Content/sources.tex

--- 2015-01-10 paper/Content/sources.tex
@@
 
+\bibitem{AntLeiv14}
+A. Leiva: \emph{MVP for Android: how to organize the presentation layer}, 2014,
+[Online]. http://antonioleiva.com/mvp-android/ (retrieved 10-Jan-2015)
+
+\bibitem{Fowler04}
+M. Fowler: \emph{Inversion of Control Containers and the Dependency Injection pattern}, 2004,
+[Online]. http://martinfowler.com/articles/injection.html (retrieved 10-Jan-2015)
+
 \bibitem{FowlerSupervisingController}

### 2015-01-10 paper/Content/solution.tex
Minor stuff in solution chapter

@@
 
-The interaction with the model is done only by the presenter. This makes the app prototype an implementation of the \emph{Passive View} kind of MVP (see \cite[p. 8]{PassiveMVC}).
+The interaction with the model is done only by the presenter. This makes the app prototype an implementation of the \emph{Passive View} kind of MVP.
 An example of an interaction sequence between objects of \texttt{Activity}, \texttt{Presenter} and \texttt{Model} classes is shown in Fig.
@@
 
-As an additional remark, the usage of the \emph{Dependency Injection} (see \cite{Fowler04}) library \emph{Dagger} should be mentioned.
+As an additional remark, the usage of the \emph{Dependency Injection} (see \cite{FowlerIoC}) library \emph{Dagger} should be mentioned.
 The library was used to resolve object dependencies, like the one which exists between an \texttt{Activity} and an \texttt{Presenter} object (and vice versa).

### 2015-01-10 paper/Content/solution.tex
App prototype testing

@@
 Locations can either be specified using a free-text search field or by pointing locations on a map, for which the \emph{Google Maps} API was used.
+
+\subsection{App Structure}
 
@@
 The MVP pattern can be applied to \emph{Fragments} the same way as it is described above for \emph{Activities}.
-Presenters of \emph{Fragment} objects most likely share their model with either other \emph{Fragments} and other \emph{Activities}.
+Presenters of \emph{Fragment} objects most likely share their model with other \emph{Fragments} and other \emph{Activities}.
 An example of this was implemented in the \texttt{WeatherDetailsActivity} of the app prototype, which shows the weather data for a selected location.
@@
 It automatically injects references of both objects into each other.
+
+\subsection{Testing the App}
+
+As mentioned before in section \ref{sec:research}, a key benefit of an MVP architecture is the increased testability of the software.
+To demonstrate this ability, some tests for the app prototype were created using the testing capabilities of the Android SDK -- the Android testing framework:
+
+\textbf{Activity Unit Test}:
+An activity object will be created in an isolated environment.
+This means that, except from the tested activity object, every other component, like the application itself, is replaced by a mock implementation.
+This includes the presenter object as well.
+Using such a mock presenter implementation allows to easily test the interaction between an activity and its presenter.
+An example would be the simulation of a button click and the assertion, if the presenter object was called correctly.
+Without having MVP in place, the isolation of an activity object would be way more complicated or may even not be possible at all.
+
+\textbf{Model Unit Test}
+As the model objects of the app prototype have no dependency to any Android related component, they are very good for being tested through unit tests.
+As described for activities above, the model object will be created in an isolated environment with a mock presenter implementation.

### 2015-01-10 paper/Content/03conclusion.tex
Framework --> SDK

@@
 
-\IEEEPARstart{I}{n} course of this research paper we have analyzed the characteristics given by the \emph{Android} Framework and have identified 
+\IEEEPARstart{I}{n} course of this research paper we have analyzed the characteristics given by the \emph{Android} SDK and have identified 
 principle components which are generally used for developing an \emph{Android} applications. Those components have been examined regarding their composition and characteristics. 
@@
 
-However, just the essential framework components have been examined regarding their MVP compatibility and used in the prototype. 
-The MVP pattern for \emph{Android} would only succeed in practice if a wide bandwidth of framework components was adaptable. 
-In course of additional research studies addressing this topic we recommend to examine further frameworks components and 
+However, just the essential SDK components have been examined regarding their MVP compatibility and used in the prototype. 
+The MVP pattern for \emph{Android} would only succeed in practice if a wide bandwidth of SDK components was adaptable. 
+In course of additional research studies addressing this topic we recommend to examine further SDK components and 
 evaluate them regarding their MVP compatibility by implementing prototypes.

### 2015-01-10 paper/Content/01introduction.tex
Minor changes

@@
 pre-installed on every new device, which currently holds over 1.4 million 
-applications (as of November 2014) \cite{AppBrainStats}.\\
+applications (as of November 2014) \cite{AppBrainStats}.
 
-%\subsection{Application Development}
+% App Development
 
@@
 
-%\subsection{Challenges in Android Development}
+% Challenges in Android Development
 
@@
 That is especially because \emph{Android} tends to lead to classes containing a lot of functionality, which often requires more effort concerning testability and extendability \cite{GangOfFour}.
-\\
 
-%\subsection{Model-View-Presenter Architecture}
+% Model-View-Presenter
 
 A modern architecture approach is Model-View-Presenter (MVP), a model introduced in 1996 to support event-driven systems \cite{TaligentMVP}.
-Its main goal is to separate the data logic from the presentation logic, thus creating software which is more flexible in terms of replacing the data model without changing the presentation part or vice versa \cite{PassiveMVC}.
-Therefor, the software is split into three parts: The \emph{Model} provides the data and means to manipulate it, the \emph{View} part is responsible to display the data, and the \emph{Presenter} contains the business logic that handles user-initiated events and issues the appropriate manipulation of the data \cite{TaligentMVP}.\\
+Its main goal is to separate the Data Management (Model) and User Interface (View-Controller), thus creating software which is more flexible in terms of replacing the \emph{Model} without changing the presentation part or vice versa \cite{PassiveMVC}.
+Potel's \emph{Model-View-Presenter} pattern consists of three components: \emph{Model}, \emph{View} and \emph{Presenter}.
+The \emph{Model} represents the domain model including the business logic.
+The \emph{View} represents the user interface and interacts with the user and displays the data.
+The \emph{Presenter} is the mediator between the business logic (Model) and the user interface (View).
+Its responsibility is to prepare the data (presentation logic), to handle user-initiated events and issues the appropriate manipulation of the data.
 
-%\subsection{Applying MVP in Android}
+% Applying MVP in Android
 
@@
 However, as the considerations in this paper show, an \emph{Android} implementation of MVP is tricky.
-Some components of the SDK have several responsibilities and make it hard to define whether they are a \emph{Model}, a \emph{View} or a \emph{Presenter} \cite{PassiveMVC}.
+Some components of the SDK have several responsibilities and make it hard to define whether they are a \emph{Model}, a \emph{View} or a \emph{Presenter}.
 
 The approach developed in this paper aims to clarify the distinction of these architectural parts.
-The findings of our research may serve as a guideline on how to apply MVP in \emph{Android} application development.\\
+The findings of our research may serve as a guideline on how to apply MVP in \emph{Android} application development.
 
-%\subsection{Research Questions}
+% Research Questions
+
 In the following sections, these questions concerning the application of MVP to \emph{Android} application development are evaluated and answered:
@@
 \begin{enumerate}[label={RQ\arabic*:}, leftmargin=0.95cm]
-\item What are the inherent characteristics given / recommended by the Android Framework? What is the current state in Android Development in accordance to the inherent framework characteristics?
-\item What are the key benefits of the Model-View-Presenter approach?
-\item How can the MVP model be applied to the Android App architecture considering framework building blocks?
+\item What are the inherent characteristics given/recommended by the \emph{Android} framework and what is the current state in \emph{Android} application development in accordance to the inherent framework characteristics?
+\item What are the key benefits of the \emph{Model-View-Presenter} approach?
+\item How can the MVP approach be applied to the Android application architecture considering framework building blocks?
 \end{enumerate}
@@
 To answer these questions, a prototypical App is built using the MVP approach.
-\todo[inline]{Outlook for each chapter?}
+
+In the next section we shortly show what core components, provided by the \emph{Android} SDK, need to be considered for our MVP implementation.
+In addition, we elaborate what types of \emph{Model-View-Presenter} approaches exist and which one we have chosen to build our App prototype.
+This is followed by an detailed explanation how we applied MVP to the Android SDK and how we built our App prototype.
+The last section concludes our findings.

### 2015-01-10 paper/Content/02research.tex
Solution chapter
Merges 'images' and 'Images'
App prototype testing
Minor changes

@@
 
-\section{Research}
+\section{MVP applied to Android Apps}
 
 \IEEEPARstart{I}{n} this chapter, the questions are answered by research. Blablablabalabalaba.
+
+Before we elaborate how we applied the MVP approach to our prototype
+
+In the next section we show in detail how we applied that shit
 
@@
 \textbf{Fragment}: Fragments split more complex parts of an activity's user interface into several smaller sub-components.
-Fragments are also used to encapsulate reusable parts of the user interface, which for example need to appear in mulitple activities.
+Fragments are also used to encapsulate reusable parts of the user interface, which for example need to appear in multiple activities.
 The official documentation of the \emph{Android} SDK defines a fragment as follows \cite{SDKFragments}:
@@
 
-\subsection{MVP's two flavors: Passive View \& Supervising Controller}
+\subsection{MVP: Passive View or Supervising Controller?}
 
-The \emph{Model-View-Presenter} (MVP) pattern was introduced in 1996 by Potel \cite{TaligentMVP} while developing a programming model for multi-tier client/server applications.
-Potel explains in his paper how to generalize the classical \emph{Model-View-Controller} (MVC) approach in order to build more complex applications.
-His idea was to decompose the MVC approach into two fundamental concepts: Data Management (Model) and User Interface (View-Controller).
-
-Like in MVC, Potel's \emph{Model-View-Presenter} pattern consists of three components: \emph{Model}, \emph{View} and \emph{Presenter}.
-The \emph{Model} represents the domain model including the business logic.
-The \emph{View} represents the user interface and interacts with the user and shows the data from the model in a certain way.
-The \emph{Presenter} is the mediator between the business logic (Model) and the user interface (View).
-Its responsibility is to prepare the data (presentation logic) in order to show it in the user interface and vice versa, to determine how user interactions are going to change the model.
+Today, when we talk about MVP, we are talking about two different types: \emph{Supervising Controller} \cite{FowlerSupervisingController} and \emph{Passive View} \cite{FowlerPassiveView}.
+Fowler retired the classic MVP approach in 2006 \cite{FowlerMvpRetirementNote} and introduced those two implementations -- see Figure \ref{fig:mvp}.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{Images/mvp}
+\includegraphics[width=0.5\textwidth]{mvp}
 \caption{Supervising Controller and Passive View}
@@
 \end{figure}
-
-Today, when we talk about MVP, we are talking about two different types: \emph{Supervising Controller} \cite{FowlerSupervisingController} and \emph{Passive View} \cite{FowlerPassiveView}.
-Fowler retired the classic MVP approach in 2006 \cite{FowlerMvpRetirementNote} and introduced those two implementations -- see Figure \ref{fig:mvp}.
 
@@
 This approach reduces the \emph{View} to an absolute minimum by using the \emph{Presenter} to handle all user input events, to update the \emph{Model} based on user interactions as well as to channel \emph{Model} changes back to the \emph{View}.
-As a result, the \emph{View} is made completely passive and is no longer responsible for updating itself from the \emph{Model}.\\
+As a result, the \emph{View} is made completely passive and is no longer responsible for updating itself from the \emph{Model}.
+
 The primary driver for \emph{Passive View} is testing. This concept allows testing to be focused on the \emph{Presenter} without needing any interaction with the chosen UI framework.
-
-\subsection{Approach to solving the problem}

### 2015-01-11 paper/Content/sources.tex
Minor stuff in solution chapter
Aktuelle Gartner Zahl

@@
 
-\bibitem{GartnerAndroid2014}
-Gartner: \emph{Gartner Says Worldwide Traditional PC, Tablet, Ultramobile and 
-Mobile Phone Shipments Are On Pace to Grow 6.9 Percent in 2014}, March 2014, 
-[Online]. http://www.gartner.com/newsroom/id/2692318 (retrieved 02-Dec-2014)
+\bibitem{GartnerAndroid2015}
+Gartner: \emph{Gartner Says Tablet Sales Continue to Be Slow in 2015}, January 2015, 
+[Online]. http://www.gartner.com/newsroom/id/2954317 (retrieved 11-Jan-2015)
 
@@
 
-\bibitem{Fowler04}
+\bibitem{FowlerIoC}
 M. Fowler: \emph{Inversion of Control Containers and the Dependency Injection pattern}, 2004,

### 2015-01-11 paper/Content/01introduction.tex
Aktuelle Gartner Zahl
lower case app

@@
 After its first presentation in 2007, the open source system started its successful journey and became the leading mobile operating system in 2010 \cite{PassiveMVC}.
-According to Gartner \cite{GartnerAndroid2014}, there will be 1.1 billion \emph{Android}-based devices sold in 2014.
+According to Gartner \cite{GartnerAndroid2015}, there will be over 1.4 billion \emph{Android}-based devices sold in 2015.
 
@@
 
-To answer these questions, a prototypical App is built using the MVP approach.
+To answer these questions, a prototypical app is built using the MVP approach.
 
 In the next section we shortly show what core components, provided by the \emph{Android} SDK, need to be considered for our MVP implementation.
-In addition, we elaborate what types of \emph{Model-View-Presenter} approaches exist and which one we have chosen to build our App prototype.
-This is followed by an detailed explanation how we applied MVP to the Android SDK and how we built our App prototype.
+In addition, we elaborate what types of \emph{Model-View-Presenter} approaches exist and which one we have chosen to build our app prototype.
+This is followed by an detailed explanation how we applied MVP to the Android SDK and how we built our app prototype.
 The last section concludes our findings.

### 2015-01-11 paper/Content/03conclusion.tex
conclusion

@@
 \IEEEPARstart{I}{n} course of this research paper we have analyzed the characteristics given by the \emph{Android} SDK and have identified 
-principle components which are generally used for developing an \emph{Android} applications. Those components have been examined regarding their composition and characteristics. 
-Applying MVP offers various benefits like a better testability [……], but the paper has shown that it is often hard to define the roles 
-of the \emph{Android} components considering MVP and to embed those components into the whole MVP model. But finally we can offer an MVP approach 
-for \emph{Android} and a corresponding prototype app demonstrating how principle \emph{Android} components can be structured for applying MVP.
+principle components which are generally used for developing \emph{Android} applications. Those components have been examined regarding their composition and characteristics. 
+Finally we can offer an MVP approach for \emph{Android} and a corresponding prototype app demonstrating how principle \emph{Android} components can be structured for applying MVP.
 

### 2015-01-11 paper/Content/sources.tex
Aligned sources

@@
 App Brain: \emph{Android Statistics -- Number of Android applications}. 
-[Online].
-http://www.appbrain.com/stats/number-of-android-apps (retrieved 02-Dec-2014)
+[Online]. http://www.appbrain.com/stats/number-of-android-apps (retrieved 02-Dec-2014)
 
@@
 Google Inc., \emph{Android Developers -- Fragments},
-[Online]. http://developer.android.com/guide/components/fragments.html(retrieved 05-Jan-2015)
+[Online]. http://developer.android.com/guide/components/fragments.html (retrieved 05-Jan-2015)
 
@@
 \bibitem{FowlerMvpRetirementNote}
-Fowler, Martin: \emph{Retirement note for Model View Presenter Pattern},
+M. Fowler: \emph{Retirement note for Model View Presenter Pattern}, 2006, 
 [Online]. http://martinfowler.com/eaaDev/ModelViewPresenter.html (retrieved 10-Jan-2015)
@@
 \bibitem{FowlerSupervisingController}
-Fowler, Martin: \emph{Supervising Controller},
+M. Fowler: \emph{Supervising Controller}, 2006, 
 [Online]. http://martinfowler.com/eaaDev/SupervisingPresenter.html (retrieved 10-Jan-2015)
@@
 \bibitem{FowlerPassiveView}
-Fowler, Martin: \emph{Passive View},
+M. Fowler: \emph{Passive View}, 2006, 
 [Online]. http://martinfowler.com/eaaDev/PassiveScreen.html (retrieved 10-Jan-2015)
 
-%\bibitem{}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
 \end{thebibliography}

### 2015-01-11 paper/Content/02research.tex
Merge
Intents

@@
 
-\section{MVP applied to Android Apps}
+\section{Research}
+\label{sec:research}
+
+% MVP applied to Android Apps
 
 \IEEEPARstart{I}{n} this chapter, the questions are answered by research. Blablablabalabalaba.
+\todo[inline]{Change me}
 
@@
 \end{quote}
+
+\textbf{Intent}: Intents are objects used for communication with the \emph{Android} system.
+An example would be the start of an activity: an intent must be created including some information to identify, which activity should be started.
+The intent will be handed over to the \emph{Android} system, which will create and start a corresponding activity.
+In the official SDK documentation, an intent is defined as \enquote{a messaging object you can use to request an action from another app component} \cite{SDKIntents}.
 

### 2015-01-11 paper/Content/solution.tex
Intents

@@
 
-As mentioned above, the basic building blocks of an Android application are \emph{Activities} and \emph{Fragments}.
+As mentioned above, the basic building blocks of an Android application are \emph{Activities}, \emph{Fragments} and \emph{Intents}.
 Applying MVP to an Android application therefore means to put attention on those components.
@@
 
-\todo[inline]{Maybe add something about Intents here}
+As \emph{Intents} are received by the activity object, they can be handled like any other view-related action (e.g.
+a click on a button).
+Whenever an intent was received by the activity, a corresponding action on the presenter object is executed -- nothing else.
+When it comes to creating intents, e.g.
+for switching to another activity, things get a bit more complicated.
+One would typically do such action inside the presenter, but intents require to be sent from a specific context, which can either be an activity or the application itself.
+This means that for creating an intent, the presenter must either address the main application object directly or go back to the activity and let the activity send the intent.
 
-This answers RQ3, showing that MVP can be applied to an Android application considering the \emph{Activity} and \emph{Fragment} building blocks.
+This answers RQ3, showing that MVP can be applied to an Android application considering the \emph{Activity}, \emph{Fragment} and \emph{Intent} building blocks.
 

### 2015-01-11 paper/Content/03conclusion.tex
Conclusion URLs

@@
 \emph{Google} developer \emph{Chris Banes} has developed the \emph{Android} app \emph{philm} basing on MVP. 
-The very demonstrative source code is offered on \emph{github} [https://github.com/chrisbanes/philm] and worth seeing. 
-Moreover there is a huge developer community on \emph{Google+} [https://plus.google.com/communities/114285790907815804707] dealing with different MVP approaches. 
-Finally, we want to draw your attention to the paper \emph{Android Passive MVC: a Novel Architecture Model for Android Application Development} 
-[Quelle] which is worth reading and has been an inspiration for our approach. Although the paper proposes an architecture which is rather MVC than MVP-based, 
+The very demonstrative source code\footnote{\emph{philm} source code: \\\url{https://github.com/chrisbanes/philm}} is offered on \emph{github} and worth seeing. 
+Moreover there is a huge developer community\footnote{\emph{Android MVP} community:\\\url{https://plus.google.com/communities/114285790907815804707}} on \emph{Google+}, dealing with different MVP approaches.
+Finally, we want to draw your attention to the paper \emph{Android Passive MVC: a Novel Architecture Model for Android Application Development} \cite{PassiveMVC}, which is worth reading and has been an inspiration for our approach.
+Although the paper proposes an architecture which is rather MVC than MVP-based,
 it offers an interesting approach how the components of an \emph{Android} app can be organized for building an MV-x structure.

### 2015-01-11 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/MockMainApplication.java
Added source code headers

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.test;
 
 import dagger.ObjectGraph;

### 2015-01-11 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/MockNavigationPresenter.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.test;
 
 import android.content.Context;

### 2015-01-11 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/ModuleActivityUnitTestCase.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.test;
 
 import android.app.Activity;

### 2015-01-11 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/favourites/FavouritesActivityTest.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.test.favourites;
 
 import android.widget.ListView;

### 2015-01-11 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/favourites/MockFavouritesModule.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.test.favourites;
 
 import javax.inject.Singleton;

### 2015-01-11 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/favourites/MockFavouritesPresenter.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.test.favourites;
 
 import android.content.Context;

### 2015-01-11 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/model/MockLocation.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.test.model;
 
 import inf.msc.yawapp.model.Location;

### 2015-01-11 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/search/MockSearchModule.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.test.search;
 
 import javax.inject.Singleton;

### 2015-01-11 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/search/MockSearchPresenter.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.test.search;
 
 import java.util.ArrayList;

### 2015-01-11 app-weather/app/src/androidTest/java/inf/msc/yawapp/test/search/SearchActivityTest.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.test.search;
 
 import android.support.v7.widget.SearchView;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/MainApplication.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp;
 
 import android.app.Application;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/MainModule.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp;
 
 import dagger.Module;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/common/BaseModuleActivity.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.common;
 
 import android.content.Context;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/common/BaseModuleFragment.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.common;
 
 import android.app.Fragment;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/common/GenericCache.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.common;
 
 public class GenericCache<T> extends GenericObservable<T> {

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/common/GenericObservable.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.common;
 
 import android.database.Observable;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/common/GenericObserver.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.common;
 
 public interface GenericObserver<T> {

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/common/Intents.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.common;
 
 public class Intents {

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/details/WeatherDetailsActivity.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.details;
 
 import android.content.Intent;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/details/WeatherDetailsModule.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.details;
 
 import javax.inject.Singleton;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/details/WeatherDetailsPresenterImpl.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.details;
 
 import android.content.Context;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/details/WeatherDetailsView.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.details;
 
 import inf.msc.yawapp.model.WeatherData;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/details/current/CurrentWeatherFragment.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.details.current;
 
 import android.graphics.Typeface;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/details/current/CurrentWeatherModule.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.details.current;
 
 import javax.inject.Singleton;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/details/current/CurrentWeatherPresenter.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.details.current;
 
 public interface CurrentWeatherPresenter {

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/details/current/CurrentWeatherPresenterImpl.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.details.current;
 
 import javax.inject.Inject;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/details/current/CurrentWeatherView.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.details.current;
 
 import inf.msc.yawapp.model.WeatherData;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/favourites/FavouritesActivity.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.favourites;
 
 import android.os.Bundle;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/favourites/FavouritesListViewAdapter.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.favourites;
 
 import android.app.Activity;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/favourites/FavouritesModule.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.favourites;
 
 import javax.inject.Singleton;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/favourites/FavouritesPresenter.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.favourites;
 
 import android.content.Context;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/favourites/FavouritesView.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.favourites;
 
 import java.util.List;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/map/MapActivity.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.map;
 
 import android.os.Bundle;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/map/MapModule.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.map;
 
 import javax.inject.Singleton;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/map/MapPresenter.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.map;
 
 import android.content.Context;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/map/MapView.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.map;
 
 public interface MapView {

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/model/CitySearchSuggestions.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.model;
 
 import java.io.BufferedReader;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/model/FavouritesStore.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.model;
 
 import java.util.List;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/model/FavouritesStoreEntry.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.model;
 
 public class FavouritesStoreEntry implements MutableLocation {

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/model/FavouritesStoreImpl.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.model;
 
 import android.content.ContentValues;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/model/FavouritesStoreOperation.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.model;
 
 public interface FavouritesStoreOperation {

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/model/Location.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.model;
 
 import java.io.Serializable;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/model/ModelModule.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.model;
 
 import javax.inject.Singleton;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/model/MutableLocation.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.model;
 
 public interface MutableLocation extends Location {

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/model/OpenWeatherMapInteractor.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.model;
 
 import android.os.AsyncTask;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/model/OpenWeatherMapWeatherData.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.model;
 
 import net.aksingh.java.api.owm.CurrentWeatherData;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/model/WeatherData.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.model;
 
 public interface WeatherData {

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/model/WeatherDataListener.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.model;
 
 public interface WeatherDataListener {

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/model/WeatherSearchInteractor.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.model;
 
 public interface WeatherSearchInteractor {

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/navigation/NavDrawerItem.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.navigation;
 
 import inf.msc.yawapp.R;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/navigation/NavDrawerListViewAdapter.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.navigation;
 
 import android.app.Activity;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/navigation/NavigationModule.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.navigation;
 
 import javax.inject.Singleton;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/navigation/NavigationPresenter.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.navigation;
 
 import android.content.Context;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/navigation/SubmitSearchInteractor.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.navigation;
 
 import inf.msc.yawapp.model.Location;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/navigation/SubmitSearchInteractorImpl.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.navigation;
 
 import android.content.Intent;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/owm/OpenWeatherMapAdapterImpl.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.owm;
 
 import net.aksingh.java.api.owm.CurrentWeatherData;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/owm/OpenWeatherMapException.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.owm;
 
 public class OpenWeatherMapException extends Exception {

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/owm/OpenWeatherMapModule.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.owm;
 
 import net.aksingh.java.api.owm.OpenWeatherMap;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/search/SearchActivity.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.search;
 
 import android.app.SearchManager;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/search/SearchModule.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.search;
 
 import javax.inject.Singleton;

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/search/SearchPresenter.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.search;
 
 public interface SearchPresenter {

### 2015-01-11 app-weather/app/src/main/java/inf/msc/yawapp/search/SearchPresenterImpl.java

@@ -1,3 +1,19 @@
+/*
+ * This source code is part of the research paper
+ * "Applying Model-View-Presenter Architecture to the Android Framework with App Prototype"
+ *
+ * Software Architecture and Management,
+ * Herman-Hollerith-Zentrum, Reutlingen University
+ *
+ * Authors:  Dennis G. Geisse,
+ *           Iven John,
+ *           Daniel Joos,
+ *           Sebastian Kotstein,
+ *           Michael Wurster
+ *
+ * Year:     2015
+ */
+
 package inf.msc.yawapp.search;
 
 import java.util.List;

### 2015-01-12 paper/Content/02research.tex
Minor corrections
minor changes

@@
 \label{sec:research}
-
+\todo[inline]{Change title?}
+\IEEEPARstart{B}{efore} the application prototype is built, composing components of \emph{Android} applications are introduced in this chapter.
+In addition, it is shown why the MVP approach may improve app development and what MVP actually is.
 % MVP applied to Android Apps
-
-\IEEEPARstart{I}{n} this chapter, the questions are answered by research. Blablablabalabalaba.
-\todo[inline]{Change me}
-
-Before we elaborate how we applied the MVP approach to our prototype
-
-In the next section we show in detail how we applied that shit
 
@@
 \subsection{Problems in Android Development (detailed)}
+\todo[inline]{Change heading and add text here}
 

### 2015-01-13 paper/Content/abstract.tex
App prototype testing
First Abstract Idea

--- 2014-12-02 paper/Content/abstract.tex
@@
 %\boldmath
-The abstract goes here.
+One of the most commonly used operating system in mobile industry is \emph{Android}.
+This paper is about development of \emph{Android} applications and describes how an Model-View-Presenter architecture can be applied to such.
+An application prototype was developed to support this paper.
 \end{abstract}

### 2015-01-13 paper/Content/solution.tex
Minor corrections
minor changes
typos

@@
 
-The prototype Android app, developed for this paper, is a simple weather app.
+\IEEEPARstart{T}{he} prototypical Android app, developed for this paper, is a simple weather app.
 It is able to show the current weather data for a location including temperature, humidity and wind.
@@
 
-Each activity object has an presenter object associated, implementing the \texttt{Presenter} interface.
+Each activity object has a presenter object associated, implementing the \texttt{Presenter} interface.
 On the other hand, the presenter object has a reference to the activity object.

### 2015-01-13 paper/Content/02research.tex
Removed todo
WIP Common Android Development Approach

@@
 \label{sec:research}
-\todo[inline]{Change title?}
 \IEEEPARstart{B}{efore} the application prototype is built, composing components of \emph{Android} applications are introduced in this chapter.
@@
 
-\subsection{Components of an \emph{Android} Application}
+\subsection{Concepts & Components of \emph{Android} Applications}
 
-Building an \emph{Android} application requires several core components of the \emph{Android} SDK to be used.
-This section gives a short overview and short explanation of the components, used for the prototype, created for this paper.
+Building \emph{Android} applications requires several core components of the \emph{Android} SDK to be used.
+This section gives a short overview and explanation of important components used in the implementation of the prototype created for this paper.
 
@@
 The official \emph{Android} SDK documentation \cite{SDKActivities} defines an activity as \enquote{an application component that provides a screen with which users can interact in order to do something}.
-There is a defined lifcycle, which all activity objects go through -- the creation, start, stop and the destruction of an activity object.
-This lifecycle is managed by \emph{Android} itself, meaning an application developer must not manually create or destroy activity objects.
+There is a defined lifcycle, which all activity objects share and follow -- the creation, start, resume, pause, stop and the destruction of an activity object.
+This lifecycle is managed by \emph{Android} itself, meaning application developers must not manually create or destroy activity objects.
 
@@
 
-\subsection{Problems in Android Development (detailed)}
-\todo[inline]{Change heading and add text here}
+\subsection{Common Android Development Approach}
+As a result of strong interrelations between its building components, the \emph{Android} system manages most of its components by itself.
+Given the complexity and interaction between these as well as the general structure, the framework steers developers toward handling tasks in common ways.
+In order to help developers understand the structure of the framework, code examples and component explanations are provided in \cite{SDKComponents}.
+
+Since the building components are managed by the system and dependent on each others implementation, one aspect that is inheritly difficult is testability.
+It is a challenge to divide business logic from the framework as it needs to react to certain system events -- as activity creation or destruction -- in order to be compatible to \emph{Android}.
+Another area
 

### 2015-01-13 paper/Content/sources.tex
Intents
WIP Common Android Development Approach

@@
 [Online]. http://developer.android.com/guide/components/fragments.html (retrieved 05-Jan-2015)
+
+\bibitem{SDKIntents}
+Google Inc., \emph{Android Developers -- Intents and Intent Filters},
+[Online]. http://developer.android.com/guide/components/intents-filters.html (retrieved 11-Jan-2015)
+
+\bibitem{SDKComponents}
+Google Inc., \emph{Android Developers -- App Components},
+[Online]. http://developer.android.com/guide/components/index.html (retrieved 11-Jan-2015)
 

### 2015-01-13 paper/Content/02research.tex
abstract proposal.
Common Android Development Approach continuation

@@
 
-\subsection{Concepts & Components of \emph{Android} Applications}
+\subsection{Concepts \& Components of Android Applications}
 
@@
 
-Since the building components are managed by the system and dependent on each others implementation, one aspect that is inheritly difficult is testability.
-It is a challenge to divide business logic from the framework as it needs to react to certain system events -- as activity creation or destruction -- in order to be compatible to \emph{Android}.
-Another area
+Since the building components are managed by the system and dependent on the implementations, one aspect that is inherently difficult is \emph{testability}.
+It is a challenge to divide business logic from the framework as it needs to react to certain system events -- like activity destruction, which may be forced by the system at any point in time and need to be appropriately handled by the developer.
+
+Other common difficulties developers face lie with the \emph{maintainability} and \emph{extensibility} of their software.
+Given the \emph{Android} framework, its many components and classes that enable communication between these compontents, the structure often gets cluttered -- especially in larger application projects.
+For example, \emph{ListView}s\footnote{Component to \enquote{display a list of scrollable items}.
+\cite{SDKListView}} need \emph{Adapter}\footnote{Class to \enquote{bridge between AdapterView and the underlying data}.
+\cite{SDKAdapter}} to display their content, which in turn might use \emph{Loader}s\footnote{Component that \enquote{performs asynchronous loading of data}.
+\cite{SDKLoader}} and \emph{Cursor}s\footnote{Interface class providing access to results of database queries.
+\cite{SDKCursor}} to fetch the data to display.
+
+In addition \emph{portability} is a problem as business logic that is strongly intertwined when developing for the \emph{Android} platform cannot easily be ported to other platforms.
 

### 2015-01-13 paper/Content/sources.tex
Common Android Development Approach continuation

@@
 
+\bibitem{SDKListView}
+Google Inc., \emph{Android Developers -- List View},
+[Online]. http://developer.android.com/guide/topics/ui/layout/listview.html (retrieved 11-Jan-2015)
+
+\bibitem{SDKAdapter}
+Google Inc., \emph{Android Developers -- Adapter},
+[Online]. http://developer.android.com/reference/android/widget/Adapter.html (retrieved 11-Jan-2015)
+
+\bibitem{SDKLoader}
+Google Inc., \emph{Android Developers -- Loader},
+[Online]. http://developer.android.com/reference/android/content/Loader.html (retrieved 11-Jan-2015)
+
+\bibitem{SDKCursor}
+Google Inc., \emph{Android Developers -- Cursor},
+[Online]. http://developer.android.com/reference/android/database/Cursor.html (retrieved 11-Jan-2015)
+
 \bibitem{BallOfMud}

### 2015-01-13 paper/Content/01introduction.tex
typos

@@
 After its first presentation in 2007, the open source system started its successful journey and became the leading mobile operating system in 2010 \cite{PassiveMVC}.
-According to Gartner \cite{GartnerAndroid2015}, there will be over 1.4 billion \emph{Android}-based devices sold in 2015.
+According to Gartner \cite{GartnerAndroid2015}, there will be over 1.4 billion \emph{Android}-based devices sold in 2015.\\
 
@@
 In addition, we elaborate what types of \emph{Model-View-Presenter} approaches exist and which one we have chosen to build our app prototype.
-This is followed by an detailed explanation how we applied MVP to the Android SDK and how we built our app prototype.
+This is followed by a detailed explanation how we applied MVP to the Android SDK and how we built our app prototype.
 The last section concludes our findings.

### 2015-01-13 paper/Content/abstract.tex

--- 2014-12-02 paper/Content/abstract.tex
@@
 %\boldmath
-The abstract goes here.
+Today, \emph{Android} is the most commonly used operating system in mobile industry.
+It allows a wide variety of architecture approaches in application development, all having their own advantages and disadvantages regarding testability, maintainability and the like.
+After introducing the basic components of \emph{Android} applications and giving an overview about the current state in \emph{Android} development, this paper describes how the Model-View-Presenter (MVP) approach can be used to develop applications that can be conveniently tested, maintained and extended.
+To support the idea presented in this paper, an Android app called \emph{Yet Another Weather App} is created using the methods described in the paper.
 \end{abstract}

### 2015-01-13 paper/Content/02research.tex
fixed merge issue
typo and citation fix

@@
 \subsection{Concepts \& Components of Android Applications}
-
 Building \emph{Android} applications requires several core components of the \emph{Android} SDK to be used.
@@
 Other common difficulties developers face lie with the \emph{maintainability} and \emph{extensibility} of their software.
-Given the \emph{Android} framework, its many components and classes that enable communication between these compontents, the structure often gets cluttered -- especially in larger application projects.
-For example, \emph{ListView}s\footnote{Component to \enquote{display a list of scrollable items}.
-\cite{SDKListView}} need \emph{Adapter}\footnote{Class to \enquote{bridge between AdapterView and the underlying data}.
-\cite{SDKAdapter}} to display their content, which in turn might use \emph{Loader}s\footnote{Component that \enquote{performs asynchronous loading of data}.
-\cite{SDKLoader}} and \emph{Cursor}s\footnote{Interface class providing access to results of database queries.
-\cite{SDKCursor}} to fetch the data to display.
+Given the \emph{Android} framework, its many components and classes that enable communication between these components, the structure often gets cluttered -- especially in larger application projects.
+For example, \emph{ListView}s\footnote{Component to \enquote{display a list of scrollable items} \cite{SDKListView}.} need \emph{Adapter}\footnote{Class to \enquote{bridge between AdapterView and the underlying data} \cite{SDKAdapter}.} to display their content, which in turn might use \emph{Loader}s\footnote{Component that \enquote{performs asynchronous loading of data} \cite{SDKLoader}.} and \emph{Cursor}s\footnote{Interface class providing access to results of database queries \cite{SDKCursor}.} to fetch the data to display.
 

### 2015-01-13 paper/Content/02research.tex
finally

@@
 Given the \emph{Android} framework, its many components and classes that enable communication between these components, the structure often gets cluttered -- especially in larger application projects.
-For example, \emph{ListView}s\footnote{Component to \enquote{display a list of scrollable items} \cite{SDKListView}.} need \emph{Adapter}\footnote{Class to \enquote{bridge between AdapterView and the underlying data} \cite{SDKAdapter}.} to display their content, which in turn might use \emph{Loader}s\footnote{Component that \enquote{performs asynchronous loading of data} \cite{SDKLoader}.} and \emph{Cursor}s\footnote{Interface class providing access to results of database queries \cite{SDKCursor}.} to fetch the data to display.
+For example, \emph{ListView}s\footnote{Component to \enquote{display a list of scrollable items} \cite{SDKListView}.} need \emph{Adapter}\footnote{Class to \enquote{bridge between AdapterView and the underlying data} \cite{SDKAdapter}.} to display their content, which in turn might use \emph{Loader}s\footnote{Component that \enquote{performs asynchronous loading of data} \cite{SDKLoader}.} and \emph{Cursor}s\footnote{Interface class providing access to results of database queries.
+\cite{SDKCursor}} to fetch the data to display.
 
